Happiness in US: Analysis of the Effects of Demographic Factors during 1972 to 2021

### 2023-03-16 outputs/paper/Happiness and demographic factors.qmd
file name changed

# Only for female
female_data <- filter(sex_data, Sex == "Female")
gfemale <- ggplot(female_data, 
       aes(y = Year, 
           fill = Happy_level)) + 
  geom_bar(position = "fill") + 
  theme_classic() +
  coord_flip()+
  labs(x = "Year", y = "Number of Respondents", fill = "Happy Level", 
       title = "Female",
       color = "Happy level")

# Only for male
male_data <- filter(sex_data, Sex == "Male")
gmale <- ggplot(male_data, 
       aes(y = Year, 
           fill = Happy_level)) + 
  geom_bar(position = "fill") + 
  theme_classic() +
  coord_flip()+
  labs(x = "Year", y = "Number of Respondents", fill = "Happy Level", 
       title = "Male",
       color = "Happy level")

@@

\newpage
# Appendix
A link to our survey exploring what will affect happiness in US can be found in the footnotes below.^[https://forms.gle/ZAoN1uFc9Gc24anh8]
And you can access our survey through the QR code below.

@@

```{r, echo=FALSE, out.width="100%"}
knitr::include_graphics(here::here("outputs/survey/survey_1.png"))
knitr::include_graphics(here::here("outputs/survey/survey_2.png"))
knitr::include_graphics(here::here("outputs/survey/survey_3.png"))
knitr::include_graphics(here::here("outputs/survey/survey_4.png"))
knitr::include_graphics(here::here("outputs/survey/survey_5.png"))
knitr::include_graphics(here::here("outputs/survey/survey_6.png"))
```
{{< pagebreak >}}
## References

>>>>

# Only for female
female_data <- filter(sex_data, Sex == "Female")
gfemale <- ggplot(female_data, 
       aes(y = Year, 
           fill = Happy_level)) + 
  geom_bar(position = "fill") + 
  theme_classic() +
  coord_flip()+
  labs(x = "Percentage", y = "Year", fill = "Happy Level", 
       title = "Female",
       color = "Happy level")

# Only for male
male_data <- filter(sex_data, Sex == "Male")
gmale <- ggplot(male_data, 
       aes(y = Year, 
           fill = Happy_level)) + 
  geom_bar(position = "fill") + 
  theme_classic() +
  coord_flip()+
  labs(x = "Percentage", y = "Year", fill = "Happy Level", 
       title = "Male",
       color = "Happy level")

@@

\newpage
# Appendix {-}
A link to our survey exploring what will affect happiness in US can be found in the footnotes below.^[https://forms.gle/ZAoN1uFc9Gc24anh8]
And you can access our survey through the QR code below.

@@

```{r, echo=FALSE, out.width="100%"}
knitr::include_graphics(here::here("outputs/survey/survey_1.png"))
knitr::include_graphics(here::here("outputs/survey/survey_2.png"))
knitr::include_graphics(here::here("outputs/survey/survey_3.png"))
knitr::include_graphics(here::here("outputs/survey/survey_4.png"))
knitr::include_graphics(here::here("outputs/survey/survey_5.png"))
knitr::include_graphics(here::here("outputs/survey/survey_6.png"))
```
{{< pagebreak >}}
# Reference {-}
